Expected Dependency Pair Match:\\ Predicting translation quality with expected syntactic structure

### 2009-05-15 mtjournal.tex
made endnotes more readable as endnotes, updated to-do

@@

  \textbf{d\_50} and \textbf{d\_50\_var} measures.\endnote{Since

@@

    weights, \textbf{d\_50} and \textbf{d\_50\_var} may be using a sum
    of counts over the 50-best list rather than expected-counts over a
    uniform distribution. These two approaches are equivalent --- so
    long as the $n$-best list is always the same length for hypothesis
    and reference.  In our implementation, the $n$-best list does not
    always reach 50 candidate parses on short sentences, so the
    expectation matches our intent better than a sum of counts over
    the $n$-best.}

@@

\subsection{Reference evaluation measures over parallel translations}

For some of the experiments presented here (sections~\ref{sec:hter1}
and~\ref{sec:hter2}), we have multiple translations of the same source
segment, each from a different translation engine and each with its
own HTER score.  For these translations, reporting correlations of
metric $m$ with absolute HTER scores can conflate $m$'s power in
identifying which of two candidate translations is better with $m$'s
(and HTER's) ability to distinguish which source segments are more
difficult to translate.

To avoid this conflation, on the HTER corpora we report correlations
on $\bar{\mu}m$ and $\bar{\mu}\textrm{HTER}$ (rather than measure
$m$ and HTER), where $\bar{\mu}$ represents mean-removal:
\begin{equation}
  \label{eq:meansub}
  \bar{\mu}m(t_i) = m(t_i) - \sum_{j=1}^I\frac{m(t_j)}{I}
\end{equation}
Mean-removal lowers the correlation $r$ values reported but ensures
that the reported correlations are among differences in the
translations rather than among differences in the underlying segments.
\endnote{ Previous work \cite{kahn08metricsmatr} reported HTER
  correlations against pairwise differences among translation segments
  derived from the same source segment. The results are similar to
  those reported here. However, we believe that pairwise differences
  introduce problems with the independence assumptions in the
  Pearson's $r$ tests, and we use mean-removal throughout this work
  instead.}

@@

For these experiments, we use LDC Multiple Translation Chinese corpus
parts 2~\cite{LDC03MTC2} and 4~\cite{LDC06MTC4}.  These corpora
include multiple human judgments of fluency and adequacy for each
sentence, with each judgment using a different human judge and a
different reference translation.  For a rough\endnote{Our segment
  count differs from \inlinecite{owczarzak07labelleddepseval}, who
  report 16,800 segments over the same corpus. We find baseline
  correlations (BLEU$_4$ and TER) lower than those reported there as
  well, so the results presented here are not directly comparable with
  that paper, though we demonstrate similar gains over those baselines
  in essentially the same
  corpus. % (section~\ref{sec:facorr:newdeps}).}
} comparison with \inlinecite{owczarzak07labelleddepseval}, we treat
each judgment as a separate segment.
%
This treatment of this corpus yields 16,815 tuples of
$\langle$hypothesis, reference, fluency, adequacy$\rangle$.  In these
experiments, we extend this tuple with automatic scores derived from
$\langle$hypothesis, reference$\rangle$ and examine the
correlations\endnote{The independence of each of these segments is
  questionable, since the same hypothesis translations are used in
  multiple items, but for the sake of methodological comparison with
  prior work, this strategy is preserved.}  between those automatic
scores and the arithmetic mean of the fluency and adequacy measures.

>>>>

\label{sec:metricdimensions}

@@

  \textbf{d\_50} and \textbf{d\_50\_var} measures.\endnote{

@@

    confidence weights, thus \textbf{d\_50} and \textbf{d\_50\_var}
    may be using a sum of counts over the 50-best list rather than
    expected-counts over a uniform distribution, as we suggest in
    section~\ref{sec:metricdimensions}. These two approaches are
    equivalent --- so long as the $n$-best list is always the same
    length for hypothesis and reference.  In our implementation, the
    $n$-best list does not always reach 50 candidate parses on short
    sentences, so the expectation matches our intent better than a sum
    of counts over the $n$-best.}

@@

\subsection{Reference evaluation measures over parallel translations}
\label{sec:metricsreference}
For some of the experiments presented here (sections~\ref{sec:hter1}
and~\ref{sec:hter2}), we have multiple translations of the same source
segment, each from a different translation engine and each with its
own HTER score.  For these translations, reporting correlations of
metric $m$ with absolute HTER scores can conflate $m$'s power in
identifying which of two candidate translations is better with $m$'s
(and HTER's) ability to distinguish which source segments are more
difficult to translate.

To avoid this conflation, on the HTER corpora we report correlations
on $\bar{\mu}m$ and $\bar{\mu}\textrm{HTER}$ (rather than measure
$m$ and HTER), where $\bar{\mu}$ represents mean-removal:
\begin{equation}
  \label{eq:meansub}
  \bar{\mu}m(t_i) = m(t_i) - \sum_{j=1}^I\frac{m(t_j)}{I}
\end{equation}
Mean-removal lowers the correlation $r$ values reported but ensures
that the reported correlations are among differences in the
translations rather than among differences in the underlying segments.
\endnote{Previous work \cite{kahn08metricsmatr} reported HTER
  correlations against pairwise differences among translation segments
  derived from the same source segment, unlike the mean-removal
  suggested in section~\ref{sec:metricsreference}. Those results are similar to
  those reported in section~\ref{sec:hter1}. However, we believe that pairwise differences
  introduce problems with the independence assumptions in the
  Pearson's $r$ tests, and we use mean-removal throughout this work
  instead.}

@@

\subsection{Corpus}
\label{sec:facorpus}
For these experiments, we use LDC Multiple Translation Chinese corpus
parts 2~\cite{LDC03MTC2} and 4~\cite{LDC06MTC4}.  These corpora
include multiple human judgments of fluency and adequacy for each
sentence, with each judgment using a different human judge and a
different reference translation.  For a rough\endnote{Our segment
  count reported in section~\ref{sec:facorpus} differs from
  \inlinecite{owczarzak07labelleddepseval}, who report 16,800 segments
  over the same corpus. We find baseline correlations (BLEU$_4$ and
  TER) lower than those reported there as well, so the results
  presented here are not directly comparable with that paper, though
  we demonstrate similar gains over those baselines in essentially the
  same corpus.
} comparison with \inlinecite{owczarzak07labelleddepseval}, we treat
each judgment as a separate segment.
%
This treatment of this corpus yields 16,815 tuples of
$\langle$hypothesis, reference, fluency, adequacy$\rangle$.  In these
experiments, we extend this tuple with automatic scores derived from
$\langle$hypothesis, reference$\rangle$ and examine the
correlations\endnote{The independence of the translation segments in
  the Multiple Translation Corpus described in
  section~\ref{sec:facorpus} is questionable, since the same
  hypothesis translations are used in multiple items, but for the sake
  of methodological comparison with prior work, this strategy is
  preserved.}  between those automatic scores and the arithmetic mean
of the fluency and adequacy measures.
